### 2017-06-08 sheets/talk-6/sheet-6.tex
Sample solution Talk 6.8

>>>>

\begin{answer}
  \begin{proof}
    We show that $S := P$ is the coproduct of $X$ and $Y$ together with the projection functions $p_1$ and $p_2$.
    First note that because $Z$ is initial $s$ and $t$ are unique maps.
    Let
    $ \xymatrix{
      X \ar[r]^{f_1} & A & Y \ar[l]_{f_2}
    } $
    be a diagramm in $\cat{A}$.
    We have to show that there is a unique map $\bar{f}' \from P \to A$ shuch that
    \[ \xymatrix{
      X \ar[rdd]_{f_1}\ar[rd]^{p_1} & & Y \ar[ldd]^{f_2} \ar[ld]_{p_2} \\
      & P \ar@{.>}[d]|{\bar{f}'} & \\
      & A &
    } \]
    commutes. We know that the diagramm
    \[ \xymatrix{
      Z \ar[r]_s \ar[d]^t & X \ar[d]_{f_1} \\
      Y \ar[r]^{f_2} & A
    } \]
    commutes because $Z$ is initial.
    Now because this square is then a pushout square there exists a unique map $\bar{f}\from P \to A$ such that
    \[ \xymatrix{
      Z \ar[r]_s \ar[d]^t & X \ar[d]_{p_1} \ar[ddr]^{f_1} & \\
      Y \ar[r]^{p_2} \ar[drr]_{f_2}& P \ar@{.>}[dr]|{\bar{f}} & \\
      & & A  \\
    } \]
    commutes. We see that we can choose $\bar{f}' := \bar{f}$.
    Suppose we have another $\tilde{f} \from P \to A$ such that
    \[ \xymatrix{
      X \ar[rdd]_{f_1}\ar[rd]^{p_1} & & Y \ar[ldd]^{f_2} \ar[ld]_{p_2} \\
      & P \ar@{.>}[d]|{\tilde{f}} & \\
      & A &
    } \]
    commutes. Then
    \[ \xymatrix{
      Z \ar[r]_s \ar[d]^t & X \ar[d]_{p_1} \ar[ddr]^{f_1} & \\
      Y \ar[r]^{p_2} \ar[drr]_{f_2}& P \ar@{.>}[dr]|{\tilde{f}} & \\
      & & A  \\
    } \]
    would also commute (because $S$ is initial) but $\bar{f}$ is unique, hence $\bar{f} = \tilde{f}$.
  \end{proof}

\end{answer}
